Supplement: Analysis and code for 'Testing Perceptual Accuracy in Charts using Surveys

### 2023-07-05 analysis/analysis.qmd
no need

---
title: "Supplement: Analysis and code for 'Testing Perceptual Accuracy in Charts using Surveys'"
format:
  jasa-html: default
  jasa-pdf:
    keep-tex: true  
    journal:
      blinded: false
date: last-modified
bibliography: references.bib 
---

>>>>

---
title: "Supplement: Analysis and code for 'Testing Perceptual Accuracy in Charts using Surveys'"
format:
  jasa-html: default
  jasa-pdf:
    include-in-header:
      - edits.tex
      - authors.tex
    keep-tex: true  
    journal:
      blinded: false
date: last-modified
bibliography: references.bib 
---
